### 2023-12-25 documentation/thesis/thesis_document.tex
more thesis

\begin{itemize}
\tightlist
\item
  ziel ist es einen low cost hallsensor-interface zu entwickeln welcher
  möglichst
\item
  universell
\item
  verschienee sensoren abbilden kann
\item
  mit verschienden magneten typen und formen nutzbar
\item
  reproduzierbar
\item
  1d, 2d, 3d
\item
  integration
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  for higher ranges analog sensoren nutzen welche jedoch eine
  aufwändigere schaltung erfodern
\item
  datenblatte links ergänzen
\item
  alle i2c in der regel, welches eine einfache integration ermöglicht
\item
  eingebauter temperatursensor ermöglicht temperaturkompensation
\item
  conrad teslameter mit seperaten temperatursensor
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  3d druck toleranztest
\item
  magnet halterung mit kraftloser arretierung
\item
  motoren und andere unter umstaänden magnetische teile in der nähe des
  sensors
\item
  nylon schrauben, 3d druck, 3d gedruckte klemmverbindungen
\item
  später rausrechnen durch kalibierung
\end{itemize}

@@

Next, the subsystem for multi-sensor
synchronisation\ref{sensor-syncronsisation-interface} is set up. The
last step in the setup is to set up communication with the host or
connected \gls{pc}. All microcontroller platforms used here have a
\gls{usb} slave port. The used usb descriptor is
\passthrough{\lstinline!Serial over (+usb)!}- ((+usb)\gls{cdc}). This is
used to emulate a virtual RS232 communication port using a USB port on a
\gls{pc} and usually no additional driver is needed on modern systems.

@@

>>>>

The main aim of this project is to develop a low-cost Hall sensor
interface that is also universally expandable. The focus is on mapping
different sensors and being compatible with different magnet types and
shapes. This ensures broad applicability in different scenarios. Another
goal is reproducibility to ensure consistent results. Easy communication
with standard PC hardware maximises the user-friendliness of the
interface. The flexibility to support different sensors and magnets
makes the system versatile and opens up possibilities for different
applications. This low-cost Hall sensor interface will therefore not
only be economically attractive, but also facilitate the integration of
Hall sensors in different contexts. In addition, the low-cost Hall
sensor interface will serve as a development platform for the data
evaluation \gls{mrp} library and provide real measurement data from
magnets. In addition, the interface firmware creates a basis for the
development of a data protocol for exchanging measured values. This
makes it easy to integrate your own measuring devices into the \gls{mrp}
ecosystem at a later date. This is only possible with a minimal
functional hardware and firmware setup and was developed for this
purpose first.

@@

The selection process for possible magnetic field sensors initially
focussed on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.
A key aspect of this selection was the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout.
The integration of integrated temperature sensors represents a
significant enhancement that will later enable precise temperature
compensation.

Linear analogue Hall sensors were deliberately omitted, although they
are suitable for more precise measurements and extended measuring
ranges. They were excluded due to the more complex circuit layouts
required and more complex power management. In the context of the
desired goal of developing a cost-efficient and universally expandable
Hall sensor interface, the decision in favour of digital sensors seems
appropriate.

@@

Focussing on digital interfaces not only facilitates implementation, but
also contributes to overall cost efficiency. At the same time, the
integration of temperature sensors enables precise measurements under
varying environmental conditions. This strategic choice forms the basis
for a flexible, universally applicable Hall sensor interface that can be
seamlessly integrated into various existing systems.

The table\ref{Implemented_digital_halleffect_sensors.csv} shows a
selection of sensors for which hardware and software support has been
implemented. The resolution of the selected sensors covers the expected
range of values required by the various magnets to be tested.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_mechanical_3D_printed_structure.png}
\caption{1D sensor mechanical 3D printed structure
\label{1D_sensor_mechanical_3D_printed_structure.png}}
\end{figure}

The mechanical structure of a sensor is kept very simple for the
following tests. The focus was on providing a stable foundation for the
sensor \gls{ic} and an exchangeable holder for different magnets.

The following figure\ref{1D_sensor_mechanical_3D_printed_structure.png},
shows a sectional view of the \gls{cad} drawing of the
\passthrough{\lstinline!1D: Single sensor!}\ref{d-single-sensor}.

All parts were produced using the 3D printing process. The sensor
circuit board was glued underneath the magnet holder. This is
interchangeable, so different distances between sensor and magnet can be
realised.

The exchangeable magnetic holder (shown in green) can be adapted to
different magnets. It can be produced quickly due to the small amount of
material used. The two recesses lock the holder with the inserted magnet
over the sensor. Due to predetermined tolerances, the magnet can be
inserted into the holder with repeat accuracy and without play. This is
important if several magnets have to be measured, where the positioning
over the sensor must always be the same.

@@

Next, the subsystem for multi-sensor
synchronisation\ref{sensor-syncronsisation-interface} is set up. The
last step in the setup is to set up communication with the host or
connected \gls{pc}. All microcontroller platforms used here have a
\gls{usb} slave port. The used usb descriptor is
\passthrough{\lstinline!Serial over (+usb)!}-((+usb)\gls{cdc}). This is
used to emulate a virtual RS232 communication port using a USB port on a
\gls{pc} and usually no additional driver is needed on modern systems.

@@

\begin{longtable}[]{@{}llllll@{}}
\caption{Measured sensor readout to processing using host software
\label{Measured_sensor_readout_to_processing_using_host_software.csv}}\tabularnewline
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright
Run\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
Datapoints\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
Host software runtime {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
Average Sensor communication time per reading {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
Communication jitter time {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
Comment\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright
Run\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
Datapoints\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
Host software runtime {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
Average Sensor communication time per reading {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
Communication jitter time {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
Comment\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.02\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
9453\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.44\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
0\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
2\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
9864\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.5\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
0\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
3\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
12984\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.22\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
0.9\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
4\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
12673\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.13\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
1.1\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
5\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
43264\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
2.19\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
4.2\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
High host system cpu load\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

The table
shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
shows various jitter measurements. These were performed on a
\passthrough{\lstinline!RaspberryPi 4 4GB!}-\gls{sbc} together with an
\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} and the
following software settings:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!Raspberry Pi OS Lite!} -
  \passthrough{\lstinline!debian bookworm x64!},
\item
  \gls{mrp}\ref{software-readout-framework}-library - version
  \passthrough{\lstinline!1.4.1!}
\item
  \passthrough{\lstinline!Unified Sensor Firmware!}\ref{unified-sensor}
  - version \passthrough{\lstinline!1.0.1!}
\end{itemize}

It can be seen that a jitter time of up to an additional
\passthrough{\lstinline!1ms!} is added between the triggering of the
measurements by the host system and the receipt of the command by the
sensor hardware. If the host system is still under load, this value
increases many times over. This means that synchronising several sensors
via the \gls{usb} connection alone is not sufficient.
